Networked Character Devices

### 2011-12-10 report/paper.tex
paper: architecture section

% Combine Architecture and System?
\section{Architecture}
\label{sec:architecture}

\lstinputlisting[float=*,
  caption={Listing Code Sample},
  label=lst:codeSample.c]{codesample.c}

\section{System}
\label{sec:system}

>>>>

\section{Architecture}
\label{sec:architecture}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{arch-03.png}
  \end{center}
  \caption{The basic client-server model of NCD.}
  \label{fig:architecture}
\end{figure}

On a very high level, NCD uses a basic client server model. The client
issues a request to the server, which in turn issues a reply. The
server never initiates any communication on its own.

\subsection{Client}

The client is currently implemented entirely within an out-of-tree kernel
module. This is arguably not the most robust, nor secure, solution. See
section \ref{sec:futurework} for details on splitting out some functionality
into a user-space helper.

Devices which have been imported on the client reside within the
devtmpfs filesystem. This is almost always mounted on \texttt{/dev}. By
default an imported device will take on the name
\texttt{/dev/netchar/importN}, where \texttt{N} is the next available
number. In the future (and without much effort), imported devices will
be able to take on their original name from the server. For example, an
input device can be located at \texttt{/dev/input/eventN}. Furthermore,
the user or administrator may choose any mapping (s)he see fits.

\subsection{Server}

The server is, as mentioned, a typical user-space daemon. It
currently only services a single file. Whether or not the server should
handle multiple exports is still up for evaluation.

The server listens on a port specified on the command line. There is no
default. When a request is received from the client, it will correspond
to one of the standard VFS file operations. Currently, \texttt{open()},
\texttt{close()}
\footnote{The counterpart for \texttt{close()} is actually referred to
as \texttt{release()} within the kernel.}
, \texttt{read()}, and \texttt{write()} are supported.

After receiving a request, the server then performs the requested
operation locally and returns the result to the client in a reply
message. For example, if the client sends an \texttt{open()} request,
the server will open and hold a file descriptor on the client's behalf.

This straightforward architecture will actually support any file type
(with certain restrictions for each type). Character devices, regular
files, sockets, and pipes should work fully (when all file operations
are implemented). Block devices and even directories will work to some
extent.

\subsection{Protocol}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{proto.png}
  \end{center}
  \caption{NCD operates over a simple request reply protocol. Bulk data
  immediately follows formal messages, as required.}
  \label{fig:protocol}
\end{figure}

The protocol is implemented as a simple request-reply system over
\texttt{INET} sockets. All request types are encapsulated within a
single request structure (see section \ref{sec:implementation}).
Similarly, there is only a single reply structure to account for all
reply types.

Bulk data is sent in the raw immediately following the corresponding
request/reply. In the case of a \texttt{read()}, the targeted data
immediately follows the reply. In the case of a \texttt{write()}, the
targeted data immediately follows the initial request.
